---
title: "Visualizations of Dataset"
subtitle: "Different visualizations"
output: html_document
author: Doris Liu
date: 2018-12-07
---

```{r setup, include=FALSE}
source("helper.R")
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(knitr)
```


## About my Dataset
This is a table from Rstudio, which is called **Titanic**. It is converted into data frame in this blog post. This dataset will be the sample that we are using to display different visualizations avaliable in R.

Below are some basic information about the data set: 

* **column names:** `r col_names`
* **head:** 
```{r, echo= FALSE}
head(my_dataframe)
```
* **number of rows:** `r num_col`


## Table

The most direct way to display data is to display the dataset as a table. 

* Package: *knitr*

we are able to display dataset as a table format, like this: 

```{r my_dataframe}
kable(my_data_head, caption = "Survival Rate for Titanic")
```

* Add caption for table by using: *caption = "caption_for_table"*.



## Line Chart

Line chart is a good way to see the trend of a series of data.

* Package: *ggplot2*

Plot a line chart, like this:

```{r}
class_survive <- my_dataframe %>% 
  group_by(Survived, Class) %>% 
  summarise("sum" = sum(Freq))
  
ggplot(class_survive, aes(Class, sum, group= class_survive$Survived)) +
  ggtitle("Survive Rate by class") +
  xlab("Survived") + ylab("Frequency") +
  geom_line(aes(col = Survived)) 
```
* Add color for lines by using: *aes(col = name_of_variable)*

## Bar Chart

Bar chart is great for showing frequencies of data and compare the numbers.

* Package: *ggplot2*

Plot a bar chart, like this: 

```{r ny_dataframe}
group_data <- my_dataframe %>% 
  group_by(Survived) %>% 
  summarise("sum" = sum(Freq))
  
ggplot(group_data) +
      geom_bar(mapping = aes(x = Survived, y = sum, fill = Survived), stat = "identity") +
      labs(title = "Rate of Survival")
```

* Add a title for chart by using: *title = "title_for_chart"*
* Fill colors for the bars by using: *are(fill = variable_name)*
